Automated Topic Naming

### 2012-01-17 ese/ese.tex
2 minor fixes

For the third set of word-lists, \textsf{exp3}, we extended the word-lists from \textsf{exp2} using unfiltered WordNet similarity matches. 
Similarity in WordNet means siblings in a hypernym tree. 
We do not include these words here for space
considerations~\footenote{For our data repository visit \url{http://softwareprocess.es/nomen/}}. 
It is not clear the words associated with our labels in \textsf{exp3} are specific enough. For example, the label \emph{maintainability} is associated with
words \emph{ease} and \emph{ownership}. In general, as we proceed from word-lists in \textsf{exp1} to that in \textsf{exp3}, our lists become more generic.

@@

Table \ref{tbl:wordlist} shows how many topics were labelled for MaxDB
and MySQL.

>>>>

For the third set of word-lists, \textsf{exp3}, we extended the word-lists from \textsf{exp2} using WordNet similarity matches. 
Similarity in WordNet means siblings in a hypernym tree. 
We do not include these words here for space
considerations~\footnote{For our data repository visit \url{http://softwareprocess.es/nomen/}}. 
Wordnet similarity is a very broad match. For example, the label \emph{maintainability} is associated with
words \emph{ease} and \emph{ownership}, and the word \emph{performance} has a `sense' which refers to musical performances -- which is not related to software development. In general, as we proceed from word-lists in \textsf{exp1} to that in \textsf{exp3}, our lists become more generic.

@@

Table \ref{tbl:wordlist} shows how many topics were labelled for MaxDB, MySQL and PostgreSQL.
